---
title: "Lab_5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Register Number:19BLC1186

Name:Tarun Sidhu

Lab Exercise No:5

Date:22/2/2021

Dataset: Cleaned_data

Task: I) For the given dataset design binary classifiers that can predict the severity level of Covid-19. Demonstrate how resampling methods can improve the estimation of the model performance.

II) For the given  dataset design binary classifiers that can predict the difficulty in breathing for Covid-19 cases. Demonstrate how model selection and regularisation techniques can be employed to improve the model accuracy.

```{r error=TRUE}
library(tidyverse)  
library(boot)  
Auto=read.csv("/Users/tarunsidhu/Desktop/Sem 4/ML/ML(Lab)/Data Sets/Cleaned-Data.csv")
names(Cleaned_Data)
ggplot(Cleaned_Data, aes(Severity_Severe,Severity_None)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), se = FALSE, linetype = 1) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, linetype = 2) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, linetype = 3)
set.seed(1)
sample <- sample(c(TRUE, FALSE), nrow(Cleaned_Data), replace = T, prob = c(0.6,0.4))
train <- Cleaned_Data[sample, ]
test <- Cleaned_Data[!sample, ]






```

