---
title: "Lab_7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Register Number:19BLC1186

Name:Tarun Sidhu

Lab Exercise No:7

Date:3/4/2021

Dataset: Cleaned-data
Design a Support Vector Machine (for the given Dataset) - Binary Classifier using Linear and Radial Kernel and Cross validation to determine optimized values for the hyper-parameters of the model.

The task is to develop a binary classifier to predict each of the severity levels of i) mild  ii) moderate  iii) severe 
```{r error=TRUE}
Cleaned.Data=read.csv("/Users/tarunsidhu/Desktop/Sem 4/ML/ML(Lab)/Data Sets/Cleaned-Data.csv")
summary(Cleaned.Data)
Cleaned_Data_1 <- Cleaned.Data[1:10000,]
attach(Cleaned_Data_1)
plot(Fever,Sore.Throat)
library(e1071)
svm.fit <- svm(Severity_Mild ~ Fever+Sore.Throat, data = Cleaned_Data_1, type='C-classification', kernel='linear', cost=10, scale=FALSE)
plot(svm.fit, Cleaned_Data_1)
summary(svm.fit)
yhat <- predict(svm.fit, Cleaned_Data_1)
table(predict=yhat, truth=Severity_Mild)
library(caret)
confusionMatrix(yhat, as.factor(Cleaned_Data_1$Severity_Mild))

```

